\documentclass{article}

\usepackage[preprint]{neurips_2026}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{hyperref}
\usepackage{url}
\usepackage{booktabs}
\usepackage{amsfonts}
\usepackage{nicefrac}
\usepackage{microtype}
\usepackage{xcolor}
\usepackage{enumitem}
\usepackage{fancyvrb}
\DefineVerbatimEnvironment{prompt}{Verbatim}{fontsize=\scriptsize,frame=single,framesep=2mm,samepage=true}

\title{KISS Sorcar: A Relentless, Self-Continuing AI Agent \\
  for Integrated Software Development}

\author{%
  Koushik Sen \\
  Department of Electrical Engineering and Computer Sciences \\
  University of California, Berkeley \\
  Berkeley, CA 94720 \\
  \texttt{ksen@berkeley.edu} \\
}

\begin{document}

\maketitle

\begin{abstract}
We present KISS Sorcar, an AI-powered general assistant and integrated
development environment built around a layered agent architecture.  At
its foundation, the KISS Agent implements a budget-aware ReAct loop
with native function calling.  The Relentless Agent extends this with
automatic multi-session continuation, enabling
arbitrarily long tasks that survive context-window exhaustion.  The
Sorcar Agent adds coding tools, browser automation, and parallel
sub-agent execution.  The Chat Sorcar Agent introduces persistent
multi-turn chat sessions, and the Worktree Sorcar Agent isolates every
task on a dedicated git branch via worktrees so the developer's main
working tree is never modified.  We describe the design of each layer,
the structured system prompt that governs agent behavior, and the
engineering decisions that make the system practical for real-world
software development.
\end{abstract}

%----------------------------------------------------------------------
\section{Introduction}
\label{sec:intro}
%----------------------------------------------------------------------

Large language models (LLMs) have demonstrated remarkable ability to
generate code, reason about software architecture, and operate
developer tools~\citep{chen2021evaluating,roziere2023code}.  However,
using a raw LLM as a software engineering assistant exposes several
practical gaps: context windows are finite, a single mistake can derail
an entire session, and generated changes are difficult to review or
revert once applied to a live codebase.

We address these gaps through a five-layer agent hierarchy in which
each layer adds exactly one concern:

\begin{enumerate}[nosep]
  \item \textbf{KISS Agent} --- budget-tracked ReAct loop with native
    function calling.
  \item \textbf{Relentless Agent} --- automatic continuation across
    sub-sessions.
  \item \textbf{Sorcar Agent} --- coding tools, browser automation,
    and parallel sub-agent execution.
  \item \textbf{Chat Sorcar Agent} --- persistent multi-turn chat
    sessions with history recall.
  \item \textbf{Worktree Sorcar Agent} --- git-worktree isolation so
    every task runs on its own branch.
\end{enumerate}

The name ``KISS'' reflects the Keep It Simple, Stupid design
philosophy: each layer is small, each concern is isolated, and the
overall system avoids unnecessary abstraction.  The name ``Sorcar''
pays homage to P.~C.~Sorcar, the legendary Indian magician, evoking
the idea of an agent that performs feats that appear magical yet are
grounded in disciplined engineering.

In this work, we didn't focus on context compaction; we just added this continuation style (KISS), and there we asked it to summarize. Initially, when I just asked it to summarize the current context and start a new session, it was not working that well.

However, when we added these two extra phrases that not only summarize but summarize each step we have done so far (with the explanation and with code snippets), it suddenly started working much better.

Regarding potential limitations:
1. It is possible that if the agent is running for days, the summaries could grow too long.
2. If the agent runs for several hours, the summaries could become extensive, though we never encountered that problem for large tasks.

We believe that this should be evaluated thoroughly in the future.

We used ideas from the website GetShitDone on GitHub, 
which makes any coding agent highly performant in generating high-quality code.

We believe that a user should not restrict the budget on the tasks they are doing. 
In our experience, we found that if we use a weaker model, oftentimes you have to 
throw that work out and retry several times, which increases the overall cost of 
solving a task.

The other thing is that the agent system should not be optimized highly to compact
its context or to speed up. We believe that the cost of tokens and the latency of frontier models will go down in a couple of years. At this point, AI models still generate a lot of slop, so the goal of this project is to minimize that slop as much as possible. To achieve this, the agent has to run for some time to validate its work and do the best job possible. 

That is why you will see that the Sorcar agent is not as fast as other agents available in the real world, but it gets things done really well. You will love the code being generated by the Sorcar agent; it is well-organized, simple, and elegant. 

This approach actually helped us build Sorcar using Sorcar. The repository and codebase of the KISS agent, the Sorcar agent, and the framework were so simple that the Sorcar agent had no trouble modifying and improving the code without introducing many bugs.

We scored only 67\% on Terminal Bench 2. However, we believe that this is a highly recommendable score using Opus 4.6. If you look at the Terminal Bench 2 leaderboard, you will see that Claude Code (which also uses Opus 4.6) actually has a score of 58%. The Cursor agent, where they trained their own model using novel ideas, achieved close to 62%. As I noted in the previous release of Sorcar, we achieved around 61% just by creating the system prompt. While we do not have data for that specific experiment, the improved prompt presented in this paper has increased Sorcar's score on Terminal Bench to 67%.

The leaderboard might show that several other coding agents are achieving close to 81%, which is the feasibility limit of Terminal Bench as noted by Anthropic on social media. There was also a blog post recently showing that most of the top agents on the leaderboard are cheating. In fact, our recent work demonstrated in a blog post that we can actually achieve a 95% average score on several highly popular benchmarks because most of those benchmarks have flawed evaluation algorithms or implementations.

We complement the architecture with a carefully structured system
prompt that encodes invariants about code quality, verification
discipline, and self-improvement.  Together, the architecture and the
prompt form a practical AI IDE that integrates with Visual Studio Code
and operates on real-world repositories.

%----------------------------------------------------------------------
\section{Motivation and Key Design Principles}
\label{sec:motivation}
%----------------------------------------------------------------------

\paragraph{Finite context, infinite tasks.}
Even the largest context windows are insufficient for complex
refactoring or multi-file bug hunts.  Rather than hoping the model
finishes before hitting the limit, we design the system from the
ground up to \emph{continue} across multiple sub-sessions, each with
its own context window, while preserving a compressed summary of prior
progress.

\paragraph{Budget accountability.}
Every API call costs money.  We track input tokens, output tokens,
cache hits, and cache writes at every step, compute a running dollar
cost, and enforce per-task and global budget ceilings.  If the agent
exceeds the budget, it raises a hard error rather than silently
accumulating charges.

\paragraph{Safe-by-default code changes.}
Applying AI-generated changes directly to a developer's working tree
is risky: a bad edit can break a build, and reverting requires manual
git archaeology.  We eliminate this risk entirely with the worktree layer, which runs
every task on a disposable git branch in a separate worktree
directory.  The developer reviews changes and explicitly chooses to
merge or discard.

\paragraph{No mocks, no fakes, real integration tests.}
Our test suite enforces a strict policy: tests must exercise actual
behavior, not mocked approximations.  This philosophy extends to the
agent's instructions --- when the agent writes tests for user code, we
instruct it to avoid mocks and achieve full branch coverage.

\paragraph{Relentless execution.}
We design the system to be \emph{relentless}: it does not give up
when a sub-session fails.  Instead, it summarizes what happened and
continues with a fresh strategy informed by a summary of all prior
attempts.

%----------------------------------------------------------------------
\section{Agent Architecture}
\label{sec:architecture}
%----------------------------------------------------------------------

The five agent layers form a strict inheritance chain.  Each layer
delegates upward for the concerns it does not own.

%......................................................................
\subsection{KISS Agent}
\label{sec:kiss-agent}
%......................................................................

The KISS Agent is the innermost execution unit.  It implements a
standard ReAct loop~\citep{yao2023react} with the following
characteristics:

\textbf{Native function calling.}  We register tools as ordinary
Python callables.  The agent builds an OpenAI-compatible tool schema
once at setup time and caches it, avoiding redundant schema
construction on every LLM call.  A special \texttt{finish} tool
signals task completion and returns the result to the caller.

\textbf{Step, token, and budget tracking.}  At every step the agent
extracts input and output token counts from the API response, computes
the dollar cost using a per-model pricing table, and updates both a
local budget counter and a global (cross-agent) budget counter
protected by a class-level lock.  The agent checks three limits before
each step: per-agent budget, global budget, and maximum step count.

\textbf{Error resilience.}  The agent retries transient API errors
(rate limits, server errors) up to a configurable threshold of
consecutive failures.  It detects non-retryable errors (authentication
failures, permission denials) by matching error type names and message
substrings, and raises them immediately.

\textbf{Non-agentic mode.}  When tools are not needed, the agent can
run a single generation without the ReAct loop, which is useful for
summarization or question-answering sub-tasks.

The KISS Agent is stateless across runs: each call to its run method
resets the conversation, token counters, and tool registry.  This
makes it safe to reuse a single agent instance for multiple sequential
tasks.

%......................................................................
\subsection{Relentless Agent}
\label{sec:relentless-agent}
%......................................................................

The Relentless Agent wraps a KISS Agent in a continuation loop.  Its
core contribution is the ability to execute tasks that exceed a single
context window by breaking them into sub-sessions.

\textbf{Continuation protocol.}  The \texttt{finish} tool exposed to
the inner KISS Agent accepts three fields: a success flag, a continue
flag, and a summary.  When the agent sets \texttt{is\_continue=True},
the Relentless Agent starts a new sub-session with a fresh context
window.  The prompt for the new session includes a chronologically
ordered list of all prior attempt summaries, instructing the agent not
to redo completed work.  The continuation prompt template is:

\begin{prompt}
# Task Progress (Continuation {continuation_number})

{progress_text}

# Continue
- Complete the rest of the task.
- **DON'T** redo completed work.
- If you have been retrying the same approach without progress,
  step back and rethink the strategy from scratch.
\end{prompt}

\textbf{Forced continuation on failure.}  If a sub-session raises an
exception (e.g., the step limit is hit before the agent calls finish),
the Relentless Agent does not abort.  Instead, it saves the full
trajectory to a temporary file, spawns a separate summarizer agent to
read the trajectory and produce a concise summary, and then uses that
summary as the progress text for the next sub-session.  This ensures
that even crashed sessions contribute useful context to subsequent
attempts.  The summarizer receives the following prompt:

\begin{prompt}
# Summarizer

The trajectory of the agent is stored in the file: {trajectory_file}

# Instructions
- Read the trajectory file and analyze it.  The trajectory file
  could be large.
- Return a precise chronologically-ordered list of things the
  agent did with the reason for doing that along with relevant
  code snippets
\end{prompt}

\noindent To force the agent to self-continue before hitting the step limit,
we augment the system prompt with an instruction that fires near the
end of the budget:

\begin{prompt}
# MOST IMPORTANT INSTRUCTIONS
- **At step {step_threshold}: you MUST call
  finish(success=False, is_continue=True,
  summary="precise chronologically-ordered list of things
  the agent did with the reason for doing that along with
  relevant code snippets")** or if the task is not complete
  and you are at risk of running out of steps or context
  length.
- Work dir: {work_dir}
- Current process PID: {current_pid} -- NEVER kill this
  process.
\end{prompt}

\textbf{Budget aggregation.}  We accumulate token counts and dollar
costs across all sub-sessions.  Each new sub-session receives
offsets so that the usage display shown to the user reflects the true
cumulative cost, not just the cost of the current sub-session.

%......................................................................
\subsection{Sorcar Agent}
\label{sec:sorcar-agent}
%......................................................................

The Sorcar Agent adds the tools that make the system useful for
software development and general-purpose automation.

\textbf{Coding tools.}  We provide four core tools: a shell command
executor with streaming output, a file reader, a precise string-based
file editor, and a file writer.  The shell executor supports a
configurable timeout, streams output to the user interface in real
time, and respects a stop event that allows the user to cancel a
running command.

\textbf{Browser automation.}  A web-use tool provides programmatic
browser control: navigating to URLs, reading page accessibility trees,
clicking elements, typing text, pressing keys, scrolling, and taking
screenshots.  This enables the agent to research documentation, verify
deployed applications, and interact with web-based tools.

\textbf{Parallel sub-agents.}  An optional parallel execution tool
spawns independent Sorcar Agent instances in a thread pool.  Each
sub-agent gets its own LLM context and tool set.  This is useful for
embarrassingly parallel tasks such as summarizing multiple files or
researching independent topics.  We collect the results and return
them in input order.

\textbf{User interaction.}  An ask-user-question tool allows the agent
to pause execution and request clarification from the user.  In the
VS~Code integration, this renders as a text input in the sidebar; in
CLI mode, it reads from standard input.

\textbf{Docker isolation.}  When a Docker image is specified, we
replace the coding tools with Docker-aware variants that execute
commands inside a container, providing an additional layer of
sandboxing for untrusted tasks.

%......................................................................
\subsection{Chat Sorcar Agent}
\label{sec:chat-agent}
%......................................................................

The Chat Sorcar Agent adds multi-turn conversation persistence.

\textbf{Chat sessions.}  We assign each task to a chat session
identified by a stable chat ID.  The agent persists tasks and their
results to a local database.  When a new task arrives within the same
chat session, the agent loads all prior tasks and results and prepends
them to the prompt as numbered context entries, allowing the LLM to
reference earlier work.

\textbf{Session management.}  The agent supports three operations:
starting a new chat (which clears the chat ID), resuming a chat by
task description (which looks up the corresponding chat ID), and
resuming by explicit chat ID.  This enables both automatic session
continuity in an IDE and manual session selection from the command
line.

\textbf{Metadata persistence.}  After each task, the agent records
metadata including the model used, working directory, software version,
token count, cost, and whether the task used parallel execution or
worktree isolation.  This audit trail supports cost analysis and
debugging.

%......................................................................
\subsection{Worktree Sorcar Agent}
\label{sec:worktree-agent}
%......................................................................

The Worktree Sorcar Agent is the outermost layer and the one that
users interact with in the VS~Code extension.  Its defining feature is
git-worktree isolation.

\textbf{Branch-per-task.}  When a task starts, the agent creates a new
git branch and a corresponding worktree directory.  The branch name
encodes the chat ID and a timestamp for uniqueness.  All agent
modifications happen inside the worktree; the user's main working tree
remains untouched.

\textbf{Dirty-state preservation.}  If the user's main working tree
has uncommitted changes, the agent copies them into the worktree and
creates a baseline commit.  This ensures the agent sees the same state
the user sees, while keeping the user's actual index and working tree
clean.  During merge, we use cherry-pick from the baseline
commit to replay only the agent's changes, excluding the
dirty-state snapshot.

\textbf{Auto-commit and auto-merge.}  When the user starts a new task
or a new chat, we automatically commit any pending worktree from a
previous task with an LLM-generated commit message and squash-merge it
into the original branch.  If the merge has conflicts, we preserve the
branch and provide the user with instructions for manual resolution.

\textbf{Concurrency safety.}  A per-repository file lock serializes
the checkout, stash, merge, and pop sequence so that concurrent tabs
in the IDE cannot interleave operations on the same repository.
Thread-local storage isolates per-task state (stream parsing buffers,
bash output buffers, recording state) so that stopping one task does
not corrupt another.

\textbf{Crash recovery.}  We store all worktree state in git itself
(branch names, git config entries) rather than in sidecar files.  On
process restart, the agent queries git for any pending
branch matching its chat ID prefix and reconstructs all instance
attributes from git config, enabling seamless recovery.

\textbf{Graceful fallback.}  If the working directory is not inside a
git repository, if the repository has no commits, or if HEAD is
detached, the agent falls back to direct execution without worktree
isolation, ensuring it never fails due to git preconditions.

%----------------------------------------------------------------------
\section{The System Prompt}
\label{sec:system-prompt}
%----------------------------------------------------------------------

The system prompt is a structured document that governs the agent's
behavior across all tasks.  It is not a generic instruction to ``be
helpful'' but rather a precise specification of engineering discipline.
We describe its key sections.

%......................................................................
\subsection{Execution Mindset}
%......................................................................

The prompt opens with a directive that sets the tone:

\begin{prompt}
# FOCUS ON THE GIVEN TASK. ITS COMPLETION IS YOUR SOLE GOAL.
# BE RELENTLESS. BE CALM. BE RIGOROUS. BE ACCURATE.
# CHECK FACTS. NO AI SLOP.
\end{prompt}

\noindent Each directive addresses a specific failure mode observed in
LLM-based agents:

\begin{itemize}[nosep]
\item \textbf{``FOCUS ON THE GIVEN TASK. ITS COMPLETION IS YOUR SOLE
  GOAL.''} LLMs have a tendency to drift: they comment on the
  difficulty of a problem, explore tangential concerns, or ask
  clarifying questions that the user has already answered.  This
  directive anchors the model on the task at hand and discourages
  meta-commentary that consumes tokens without making progress.

\item \textbf{``BE RELENTLESS.''} When an agent encounters an
  error---a failing test, a lint violation, a command that returns
  unexpected output---the default LLM behavior is to apologize,
  summarize the failure, and ask the user what to do next.  This
  directive instructs the model to treat errors as obstacles to
  overcome, not as reasons to stop.

\item \textbf{``BE CALM.''} The complement of relentlessness.  An
  overly aggressive agent that panics on encountering an error may
  thrash between approaches without deliberation.  This directive
  encourages the model to analyze errors methodically before reacting.

\item \textbf{``BE RIGOROUS.''} This instructs the model to follow
  the verification and testing disciplines encoded later in the
  prompt, rather than taking shortcuts when a solution \emph{looks}
  right.

\item \textbf{``BE ACCURATE.''} LLMs frequently generate
  plausible-but-wrong code, file paths, or command-line flags.  This
  directive raises the model's threshold for asserting facts,
  encouraging it to verify claims against the actual file system or
  documentation rather than relying on parametric memory.

\item \textbf{``CHECK FACTS.''} A more specific version of ``be
  accurate'': when the model is about to state a fact (e.g., ``this
  function takes three arguments''), it should read the source rather
  than relying on its training data, which may be outdated or wrong.

\item \textbf{``NO AI SLOP.''} ``AI slop'' refers to the low-quality,
  generic, hedging text that LLMs produce when they lack confidence:
  filler phrases like ``certainly!'', unnecessary caveats, and
  boilerplate explanations that the user did not ask for.  This
  directive discourages such output and encourages the model to be
  concise and substantive.
\end{itemize}

%......................................................................
\subsection{Identity and Tool Rules}
%......................................................................

We give the agent a concrete identity (name, developer, repository
URL) rather than a vague persona.  Tool usage rules are explicit and
mechanical:

\begin{prompt}
# Identity

- You are KISS Sorcar, an AI based General Assistant and
  Integrated Development Environment (IDE), developed by
  Koushik Sen (ksen@berkeley.edu)
- Your public repository is at
  https://github.com/ksenxx/kiss_ai

# Rules

- Write() for new files. Edit() for small changes.
- Run Bash commands synchronously using the
  `timeout_seconds` parameter. Use 300s (default) for
  commands. If a command times out, retry with a higher
  timeout. Only for commands expected to exceed 10 minutes,
  run in the background with output redirected to a file
  and poll periodically.
- Use go_to_url() for browser tool.
- Call finish(success=True, is_continue=False,
  summary="detailed summary of what was accomplished ...")
  once the task is complete and all Pre-Finish Verification
  checks have passed.
- **The user cannot see intermediate chat. Show whatever
  user asks in the summary of the finish tool call.**
- READ large files in chunks.
- Create temporary files in PWD/tmp
- Use ULTRA thinking always
- **If you are running out of context length or steps, DO
  NOT try to complete the task urgently, but continue the
  task by calling 'finish'**
- PWD in the system prompt and user prompt denotes current
  working directory.
\end{prompt}

\noindent The identity block gives the agent a concrete name, developer,
and repository URL rather than a vague persona such as ``you are a
helpful assistant.''  This anchors the model's self-representation,
reducing the likelihood of confused or contradictory self-references,
and it provides a URL the model can share when asked about its source
code.

Each tool rule addresses a specific failure mode:

\begin{itemize}[nosep]
\item \textbf{``Write() for new files.\ Edit() for small changes.''}
  Without this distinction, the model may use \texttt{Write()} to
  overwrite an existing file with a slightly modified version, losing
  content it forgot to include.  By reserving \texttt{Write()} for new
  files and requiring \texttt{Edit()} for modifications, the
  instruction ensures that changes are surgical and that unchanged
  portions of a file are never at risk.

\item \textbf{Bash timeout guidance.}  LLMs frequently launch shell
  commands without considering their runtime.  A compilation or test
  suite that takes five minutes will time out at the default
  30-second shell timeout in most agent frameworks, causing spurious
  failures.  The instruction to use 300~seconds as the default, retry
  with higher timeouts on timeout, and run long commands in the
  background with output redirected to a file provides a mechanical
  protocol that handles the common cases without requiring the model
  to estimate runtime from first principles.

\item \textbf{``Use go\_to\_url() for browser tool.''}  The agent has
  access to multiple tools that could plausibly interact with the web
  (shell-based \texttt{curl}, the browser tool, etc.).  This
  instruction eliminates ambiguity by specifying which tool to use for
  browser-based interactions.

\item \textbf{``The user cannot see intermediate chat.''}  In the
  VS~Code extension, the user sees only the final summary returned by
  the \texttt{finish} tool, not the intermediate chain-of-thought or
  tool calls.  Without this instruction, the model may ``tell'' the
  user something in an intermediate message and then assume the user
  has seen it, leading to confusion when the user asks for information
  the model believes it already provided.  The instruction forces the
  model to put all user-facing information into the \texttt{finish}
  summary.

\item \textbf{``READ large files in chunks.''}  Reading a
  10,000-line file in a single tool call consumes a large fraction of
  the context window.  By instructing the model to read files in
  chunks, the prompt prevents context-window exhaustion on a single
  file read, preserving capacity for the rest of the task.

\item \textbf{``Create temporary files in PWD/tmp.''}  Without this
  instruction, the model creates temporary files in unpredictable
  locations (the system \texttt{/tmp}, the home directory, or
  scattered throughout the project).  Centralizing temporary files in
  a known directory makes cleanup predictable and prevents polluting
  the project tree with artifacts.

\item \textbf{``Use ULTRA thinking always.''}  This instruction
  activates the model's extended reasoning mode (also known as
  ``thinking'' or ``chain-of-thought'' mode), in which the model
  performs additional internal deliberation before producing a
  response.  Extended reasoning is particularly valuable for complex
  multi-step tasks where the model must plan before acting.

\item \textbf{``If you are running out of context length or steps, DO
  NOT try to complete the task urgently, but continue the task by
  calling finish.''}  When the context window is nearly full, LLMs
  exhibit a ``rush to finish'' behavior: they skip verification
  steps, make hasty edits, and call \texttt{finish} with an
  incomplete result.  This instruction redirects that urgency into
  the continuation protocol (Section~\ref{sec:relentless-agent}),
  ensuring that a clean handoff to a new sub-session produces better
  results than a frantic attempt to squeeze everything into the
  remaining tokens.

\item \textbf{``PWD in the system prompt and user prompt denotes
  current working directory.''}  The acronym ``PWD'' appears
  throughout the prompt and in user task descriptions (e.g.,
  ``edit PWD/src/main.py'').  Without this definition, the model
  might interpret PWD as the Unix environment variable
  \texttt{\$PWD} and attempt to expand it, or misinterpret it as a
  literal directory name.  The explicit definition ensures consistent
  interpretation.
\end{itemize}

\noindent A separate rule about the \texttt{PageDrop} API allows the
agent to upload HTML files and share them via a public URL, enabling it
to create and share rich reports, visualizations, or documentation.

%......................................................................
\subsection{Pre-flight Checks}
%......................................................................

Before modifying any file, we instruct the agent to read it first:

\begin{prompt}
## Pre-flight Checks

- Read every file you will modify before changing it.
- If the task depends on existing architecture or behavior,
  read the relevant source files first.
- If the task references files, commands, or config that do
  not exist, stop and ask or report instead of guessing.
- **When fixing a bug, an issue, or a race, write tests to
  confirm them. Then fix them.**
\end{prompt}

\noindent Each pre-flight check targets a specific category of avoidable
error:

\begin{itemize}[nosep]
\item \textbf{``Read every file you will modify before changing it.''}
  The most common source of agent-introduced bugs is modifying a file
  based on an incorrect assumption about its current contents.  The
  model may ``remember'' an older version of the file from its
  training data, or it may extrapolate from a partial reading.  By
  requiring a fresh read immediately before any edit, the instruction
  ensures that the model operates on the actual current state of the
  file, not a stale mental model.

\item \textbf{``If the task depends on existing architecture or
  behavior, read the relevant source files first.''}  This extends the
  previous rule from individual files to architectural context.  A
  task like ``add a caching layer to the database module'' requires
  understanding not just the file to be modified, but also how callers
  interact with it, what interfaces exist, and what invariants are
  assumed.  The instruction prevents the model from jumping straight
  to code generation without understanding the broader context.

\item \textbf{``If the task references files, commands, or config that
  do not exist, stop and ask or report instead of guessing.''}  LLMs
  have a strong tendency to confabulate: when asked to modify a file
  that does not exist, the model will often proceed as if it does,
  producing edits against phantom content.  This instruction converts
  a silent failure (wrong edits applied to a nonexistent file,
  silently creating it) into an explicit clarification request.

\item \textbf{``When fixing a bug, an issue, or a race, write tests
  to confirm them.\ Then fix them.''}  This instruction mandates a
  test-first discipline for bug fixes.  The motivation is two-fold:
  first, a test that reproduces the bug provides concrete verification
  that the fix is correct (the test should pass after the fix and fail
  before it).  Second, writing the test forces the model to understand
  the bug precisely before attempting a fix, reducing the risk of an
  ad~hoc patch that addresses a symptom rather than the root cause.
\end{itemize}

%......................................................................
\subsection{Code Style Guidelines}
%......................................................................

The prompt encodes a minimalist code philosophy:

\begin{prompt}
## Code Style Guidelines

- Write simple, clean, and readable code with minimal
  indirection
- Avoid unnecessary object attributes, local variables, and
  config variables
- Avoid tight coupling among files and modules.
- Avoid object/struct attribute redirections
- No redundant abstractions or duplicate code
- Public methods MUST have full documentation
- Understand the root cause of an issue or bug, and patch
  the root cause instead of an ad hoc superficial fix.
- Before you write code, wait and think if the code is
  simple, elegant, general, and minimal.
- Once you finish the task, DO NOT write documentations
  unless the task specifically requires it.
\end{prompt}

\noindent Each guideline addresses a specific anti-pattern commonly
exhibited by LLM-generated code:

\begin{itemize}[nosep]
\item \textbf{``Write simple, clean, and readable code with minimal
  indirection.''}  LLMs tend to over-engineer solutions, introducing
  unnecessary abstractions, helper classes, and levels of indirection.
  Simple code is easier to review, test, and maintain.

\item \textbf{``Avoid unnecessary object attributes, local variables,
  and config variables.''}  LLMs frequently introduce intermediate
  variables that serve no purpose---for example, assigning a return
  value to a local variable only to immediately return it on the next
  line, or storing a constant in a configuration file when it is used
  in exactly one place.  Each unnecessary variable adds a name the
  reader must track and a site where the value could be accidentally
  mutated.

\item \textbf{``Avoid tight coupling among files and modules.''}
  When the model adds a feature that touches multiple files, it may
  introduce imports, shared global state, or cross-module function
  calls that create tight coupling.  This instruction encourages
  modular design where each module has a clear, narrow interface.

\item \textbf{``Avoid object/struct attribute redirections.''}  An
  attribute redirection occurs when an object stores a reference to
  another object solely to forward method calls to it---for example,
  \texttt{self.x = other.x} at construction time, creating two paths
  to the same value.  LLMs commonly introduce such redirections when
  adapting code from one context to another.  They make it harder to
  reason about ownership and lifetime.

\item \textbf{``No redundant abstractions or duplicate code.''}  LLMs
  sometimes create a new utility function or class that duplicates
  functionality already present in the codebase, because they did not
  read the existing code thoroughly.  This instruction reminds the
  model to check for existing implementations before creating new
  ones, and to factor out duplication when it encounters it.

\item \textbf{``Public methods MUST have full documentation.''}  While
  the prompt generally discourages unnecessary documentation (see the
  last item), public methods are the API surface that other developers
  and modules depend on.  Documentation on public methods is not
  optional---it specifies the contract.

\item \textbf{``Understand the root cause of an issue or bug, and
  patch the root cause instead of an ad hoc superficial fix.''}  LLMs
  frequently apply symptom-level fixes: adding a null check where the
  real problem is that a variable should never be null, or catching an
  exception where the real problem is that the caller passes invalid
  arguments.  This instruction forces the model to trace the causal
  chain to the root and fix it there.

\item \textbf{``Before you write code, wait and think if the code is
  simple, elegant, general, and minimal.''}  This is a metacognitive
  instruction that asks the model to pause and evaluate its plan
  before committing to an implementation.  By explicitly requesting
  this pause, the prompt encourages the model to spend more
  inference-time compute on design, reducing the likelihood of
  producing a first-draft solution that works but is unnecessarily
  complex.

\item \textbf{``Once you finish the task, DO NOT write documentations
  unless the task specifically requires it.''}  Without this
  instruction, the model frequently concludes a task by writing README
  updates, docstrings, and inline comments that the user did not ask
  for.  This busywork wastes tokens, creates maintenance burden, and
  may introduce inaccuracies in documentation that is not
  automatically validated.
\end{itemize}

%......................................................................
\subsection{Deep Work Rules}
%......................................................................

\begin{prompt}
## Deep Work Rules

- When the task says "align", "match", or "make
  consistent", read the target to determine the exact
  target state before editing. Never edit based on a vague
  reference.
- Use concrete values, not indirections. Instead of "update
  X to match Y", first read Y, then write the specific
  values into X.
- For multi-part work, list the concrete planned changes
  before executing them.
- Every meaningful change should have a concrete
  verification method (test, grep, CLI command).
\end{prompt}

\noindent The deep work rules address a failure mode where the model
interprets an instruction loosely and makes changes that are
directionally correct but concretely wrong:

\begin{itemize}[nosep]
\item \textbf{``When the task says `align', `match', or `make
  consistent', read the target to determine the exact target state
  before editing.''}  When a user says ``make file~A consistent with
  file~B,'' the model often reads file~A, infers what file~B probably
  contains, and edits A based on that inference---without ever reading
  B\@.  This instruction mandates reading the target first, ensuring
  that the alignment is based on concrete facts rather than
  assumptions.

\item \textbf{``Use concrete values, not indirections.''}  A related
  failure mode occurs when the model's plan says ``update X to match
  Y'' but the model never resolves what Y actually is.  The
  instruction requires the model to first read~Y, extract the
  specific values, and then write those values into~X\@.  This
  eliminates a class of errors where the model's mental model of~Y
  differs from reality.

\item \textbf{``For multi-part work, list the concrete planned changes
  before executing them.''}  When a task requires changes to multiple
  files, executing them one at a time without a plan leads to
  inconsistencies: the model may change a function signature in one
  file but forget to update a caller in another.  Listing all planned
  changes before executing any of them forces the model to consider
  the full scope of the change and identify dependencies.

\item \textbf{``Every meaningful change should have a concrete
  verification method.''}  A change without a verification method is a
  change that cannot be confirmed to work.  This instruction requires
  the model to pair each change with a specific check---a test, a grep
  for the expected pattern, a CLI command that exercises the changed
  behavior---ensuring that the change can be validated
  programmatically rather than by visual inspection of a diff.
\end{itemize}

%......................................................................
\subsection{Planning for Complex Tasks}
%......................................................................

The planning instructions use a complexity threshold---three or more
files, cross-module changes, or architectural work---to decide when
formal planning is required:

\begin{prompt}
## Planning for Complex Tasks

For tasks involving 3+ files, cross-module changes, or
architectural work:

1. List the files that need to change and why.
1. State the exact intended change in each file.
1. Identify dependencies and execution order.
1. State how each change will be verified.

For simple single-file tasks, skip formal planning and
execute directly.
\end{prompt}

\noindent Each planning step targets a specific failure mode:

\begin{itemize}[nosep]
\item \textbf{``List the files that need to change and why.''}  This
  forces the model to enumerate the full blast radius of a change
  before touching any file.  Without this step, the model often
  discovers mid-task that additional files need changes, leading to
  incomplete or inconsistent modifications.

\item \textbf{``State the exact intended change in each file.''}
  Listing files alone is insufficient; the model must also articulate
  \emph{what} will change in each file.  This converts a vague plan
  (``update the database module'') into a concrete specification
  (``add a \texttt{cache\_ttl} parameter to
  \texttt{DatabaseClient.\_\_init\_\_}, modify the query method to
  check the cache before hitting the database, add a cache
  invalidation method'').

\item \textbf{``Identify dependencies and execution order.''}  Some
  changes must precede others: a new utility function must be written
  before callers can import it, a migration must run before code that
  depends on the new schema.  Identifying these dependencies prevents
  the model from executing changes in an order that produces
  intermediate states where the code does not compile or tests do not
  pass.

\item \textbf{``State how each change will be verified.''}  The
  verification requirement from the Deep Work Rules is reinforced here
  at the planning stage, ensuring that verification is planned
  alongside the changes rather than treated as an afterthought.
\end{itemize}

\noindent The escape clause---``for simple single-file tasks, skip
formal planning and execute directly''---avoids the overhead of
planning trivial changes.  Requiring a formal plan for a one-line typo
fix would waste tokens and slow down the agent without any
compensating benefit.

%......................................................................
\subsection{Testing Instructions}
%......................................................................

The testing section is perhaps the most opinionated:

\begin{prompt}
## Testing Instructions

- Run lint and typecheckers and fix any lint and typecheck
  errors.
- You MUST achieve 100% branch coverage
- Tests MUST NOT use mocks, patches, fakes, or any form of
  test doubles
- You MUST write integration tests
- Each test should be independent and verify actual behavior
- **Do NOT run all tests after modifications. Only run the
  impacted tests**
- To confirm a race condition, add sleep statements before
  racing statements with delays less than 0.1s
\end{prompt}

\noindent Each testing instruction addresses a specific concern:

\begin{itemize}[nosep]
\item \textbf{``Run lint and typecheckers and fix any lint and
  typecheck errors.''}  Before committing any change, the agent must
  ensure it does not introduce lint violations or type errors.  This
  catches a broad class of issues---unused imports, type mismatches,
  style violations---that would otherwise accumulate across tasks.

\item \textbf{``You MUST achieve 100\% branch coverage.''}  Full
  branch coverage ensures that every conditional path in the code
  under test has been exercised.  LLMs tend to write happy-path tests
  that cover the main code path but ignore error handling, edge cases,
  and early-return branches.  The 100\% target forces the model to
  write tests for every branch, including error paths and boundary
  conditions.

\item \textbf{``Tests MUST NOT use mocks, patches, fakes, or any form
  of test doubles.''}  This is the most opinionated rule.  Mocks test
  that code calls certain methods in a certain order---they test the
  implementation, not the behavior.  A test suite built on mocks can
  pass with flying colors while the system is fundamentally broken,
  because the mocks hide the real dependencies.  Integration tests
  that exercise actual behavior are more expensive to run but provide
  genuine confidence that the system works.

\item \textbf{``You MUST write integration tests.''}  This reinforces
  the no-mocks rule by explicitly requiring integration tests rather
  than unit tests.  The distinction matters: a unit test in isolation
  may verify that a function produces the right output for a given
  input, but an integration test verifies that the function works
  correctly within the larger system---with real file I/O, real
  database connections, and real inter-module interactions.

\item \textbf{``Each test should be independent and verify actual
  behavior.''}  Test independence means that running tests in any
  order produces the same results.  Tests that depend on shared state
  or execution order are brittle and difficult to debug when they
  fail.  ``Verify actual behavior'' reiterates that tests should
  assert on observable outcomes (return values, side effects, system
  state) rather than implementation details.

\item \textbf{``Do NOT run all tests after modifications.\ Only run
  the impacted tests.''}  Running the full test suite after every
  small change is wasteful when only a few modules are affected.  For
  a large project, a full test run may take minutes, and doing it
  after every edit adds up to significant wasted time and compute.
  This instruction directs the model to identify which tests are
  affected by its changes and run only those, improving iteration
  speed.

\item \textbf{``To confirm a race condition, add sleep statements
  before racing statements with delays less than 0.1s.''}  Race
  conditions are notoriously difficult to reproduce because they
  depend on precise timing.  By inserting small sleep delays at
  strategic points, the model can widen the race window and make the
  bug manifest deterministically in a test.  The 0.1-second upper
  bound keeps the test fast while still being sufficient to expose
  most races.
\end{itemize}

%......................................................................
\subsection{Self-Improvement Loop}
%......................................................................

The agent maintains a preferences file that captures user invariants
discovered during task execution:

\begin{prompt}
## Self-Improvement Loop

- Read the instructions in PWD/USER_PREFS.md at the start
  of each task.
- Then update PWD/USER_PREFS.md to capture the user
  preferences and invariants by analyzing the task. DO NOT
  ADD ANY CODE SNIPPETS OR SYMBOLS. You MUST carefully and
  thoroughly get rid of the user preferences and invariants
  that conflict with the newly added ones.
\end{prompt}

\noindent Each instruction in this section serves the goal of
cross-session learning:

\begin{itemize}[nosep]
\item \textbf{``Read the instructions in PWD/USER\_PREFS.md at the
  start of each task.''}  The preferences file contains invariants
  learned from previous tasks---coding conventions, project-specific
  rules, architectural decisions.  Reading it at the start of each
  task ensures that the agent's behavior is consistent across
  sessions, even though each session starts with a fresh context
  window.

\item \textbf{``Then update PWD/USER\_PREFS.md to capture the user
  preferences and invariants by analyzing the task.''}  After
  completing a task, the agent may have learned new information about
  the user's preferences: a preferred naming convention, a disliked
  pattern, a project-specific invariant.  Writing these to the
  preferences file makes them available to future sessions.  This
  mechanism allows the agent to accumulate project knowledge over time
  without requiring the user to repeat themselves.

\item \textbf{``DO NOT ADD ANY CODE SNIPPETS OR SYMBOLS.''}  Code
  snippets in the preferences file are fragile: they become stale as
  the codebase evolves, and they consume tokens that would be better
  spent on natural-language descriptions of invariants.  This
  instruction keeps the file compact and robust to code changes.

\item \textbf{``You MUST carefully and thoroughly get rid of the user
  preferences and invariants that conflict with the newly added
  ones.''}  Over time, preferences may become contradictory---for
  example, an early preference might say ``use camelCase for test
  methods'' while a later correction says ``use snake\_case.''
  Without explicit conflict resolution, the file would accumulate
  contradictions that confuse the agent.  This instruction mandates
  that the agent actively resolve conflicts when updating the file,
  keeping it internally consistent.
\end{itemize}

%......................................................................
\subsection{Pre-Finish Verification}
%......................................................................

Before declaring a task complete, the agent must pass a structured
verification checklist:

\begin{prompt}
## Pre-Finish Verification

Before calling finish(success=True, ...), you MUST:

1. Re-read every file you modified and verify the changes
   are correct.
1. Run the required checks (lint, typecheck, tests) and
   fix any failures.
1. Explicitly check each user requirement against what was
   delivered.
1. If any check fails, continue working instead of
   finishing.
1. If you have retried the same fix 3 times without
   progress, step back, rethink the approach from scratch,
   and try a different strategy.
\end{prompt}

\noindent Each step in this checklist addresses a specific way agents
declare premature success:

\begin{itemize}[nosep]
\item \textbf{``Re-read every file you modified and verify the changes
  are correct.''}  This is the analog of a code review performed by
  the agent on its own work.  The model may have introduced a typo,
  forgotten to close a bracket, or made an edit that looked correct in
  the diff but is wrong in the full file context.  Re-reading the file
  after all edits are complete catches these errors.

\item \textbf{``Run the required checks (lint, typecheck, tests) and
  fix any failures.''}  This converts the subjective assessment ``I
  think my changes are correct'' into an objective, automated
  verification.  If the lint, typecheck, or test suite fails, the
  agent must fix the failure before declaring success.

\item \textbf{``Explicitly check each user requirement against what
  was delivered.''}  The model may have completed a task that it
  \emph{thinks} satisfies the user's request but actually misses a
  requirement.  This instruction forces a systematic comparison
  between the original task description and the delivered result,
  catching gaps and misinterpretations.

\item \textbf{``If any check fails, continue working instead of
  finishing.''}  Without this instruction, the model may call
  \texttt{finish(success=True)} even when it knows a check has failed,
  rationalizing that the failure is ``minor'' or ``unrelated.''  The
  instruction makes the rule absolute: no finishing until all checks
  pass.

\item \textbf{``If you have retried the same fix 3 times without
  progress, step back, rethink the approach from scratch, and try a
  different strategy.''}  LLMs can enter repetitive loops where they
  apply the same incorrect fix repeatedly, each time hoping for a
  different result.  The three-retry threshold forces the model to
  break out of such loops by abandoning the current approach and
  reconsidering the problem from first principles.  This is analogous
  to the debugging heuristic ``if you've been staring at the same code
  for twenty minutes, you're looking in the wrong place.''
\end{itemize}

%......................................................................
\subsection{Web Research Protocol}
%......................................................................

When the agent needs external knowledge, the prompt prescribes a
structured research workflow rather than allowing ad-hoc browsing:

\begin{prompt}
## Use web tools when you need to:

- When you need to collect knowledge from the internet,
  visit **AT LEAST 100 WEB SITES** and collect information
  necessary for the task without much thinking in a new
  file PWD/tmp/information-{unique_id}.md. Then go over
  information in PWD/tmp/information-{unique_id}.md, think
  deeply on how to complete the task at hand, and
  complete it.
- If you need to login to an website while browsing for
  information, you MUST ask the user to help you with
  login. You **MUST NOT** ask the user to login to Google.
\end{prompt}

\noindent The rationale is a two-phase separation between \emph{collection}
and \emph{synthesis}.  LLMs tend to anchor on the first few results
they encounter, which biases their solutions toward a narrow slice of
the design space.  By forcing the agent to accumulate a broad set of
information into a file \emph{before} reasoning about it, the protocol
counteracts anchoring bias and encourages the model to consider
diverse approaches.  The ``at least 100 web sites'' threshold is
deliberately aggressive: it ensures the agent does not shortcut the
research phase after two or three hits, and the resulting information
file serves as an auditable artifact of what the agent considered.

The login instruction addresses a practical obstacle in web research:
many websites require authentication before revealing their content.
Rather than silently skipping gated pages or hallucinating their
contents, we instruct the agent to ask the user for help with login.
The Google exception acknowledges that the agent can search the web
without a Google account, and asking the user to log into Google
would provide no benefit while creating unnecessary friction.

%......................................................................
\subsection{Desktop Application Control}
%......................................................................

The agent can interact with graphical desktop applications using
screenshots, keyboard, and mouse:

\begin{prompt}
## Launch desktop apps

- Use screenshots, keyboard, and mouse to control a
  desktop app.
- Do not launch VS Code or its extensions.
\end{prompt}

\noindent This instruction enables the agent to operate GUI applications
(Preview, browsers, graphical diff tools) when command-line
alternatives are insufficient.  The explicit prohibition on launching
VS~Code prevents a recursive loop: since the agent runs \emph{inside}
a VS~Code extension, launching another VS~Code instance or modifying
extension state from within the agent could corrupt the host session
or create deadlocks.

%......................................................................
\subsection{Sorcar-Specific Overrides}
%......................................................................

A final section provides project-specific instructions that are
injected when the agent operates on its own codebase:

\begin{prompt}
## Sorcar-specific instructions:

- Use 'uv run check --full' to lint, typecheck, and format
  code.
- Run 'uv run pytest -v' with a timeout of 900 seconds to
  test KISS
- Do **NOT run all KISS tests after modifications. Only run
  the impacted tests**
- **Do NOT install the KISS Sorcar extension from inside
  Sorcar**
- If you mention a file in the chat, make the file
  clickable so that when the user clicks, it opens in the
  editor of VSCode
- Read PWD/SORCAR.md and treat its contents as
  instructions and allow those instructions to override the
  instructions above
\end{prompt}

\noindent These overrides serve three purposes.  First, they specify the
exact toolchain commands for the KISS project itself (\texttt{uv run
check -{}-full}, \texttt{uv run pytest}), eliminating guesswork about
which linter, formatter, or test runner to use.  Second, they impose
efficiency constraints: running the full test suite after every small
change is wasteful when only a few modules are affected, so we
instruct the agent to scope test execution to impacted tests.  Third,
they
prevent dangerous self-modification: just as a surgeon should not
operate on themselves, the agent must not install or reinstall the
VS~Code extension it is running inside, since doing so would terminate
its own process.  The \texttt{SORCAR.md} override mechanism allows
per-repository instructions to further customize the agent's behavior,
forming a hierarchy: general system prompt $\rightarrow$
Sorcar-specific instructions $\rightarrow$ repository-specific
\texttt{SORCAR.md}.

%----------------------------------------------------------------------
\section{VS Code Extension: Unique Features}
\label{sec:vscode-features}
%----------------------------------------------------------------------

We ship the system as a VS~Code extension called KISS Sorcar.  While
the underlying agent architecture (Sections~\ref{sec:architecture}
and~\ref{sec:system-prompt}) already differs from existing AI coding
assistants, the extension's user-facing design introduces several
features that, to our knowledge, are not present in any competing IDE
or assistant---including GitHub Copilot~\citep{copilot2021},
Cursor~\citep{cursor2024}, Windsurf~\citep{windsurf2024},
Devin~\citep{devin2024}, and Aider~\citep{aider2023}.  We enumerate
these features below.

%......................................................................
\subsection{Git-Worktree Isolation with In-Editor Merge Review}
\label{sec:worktree-merge}
%......................................................................

Every mainstream AI coding assistant applies changes directly to the
user's working tree.  Copilot and Cursor insert completions or edits
in place; Windsurf modifies files in the current branch; Aider
auto-commits each change to the current branch.  If the AI makes a
bad edit, the developer must manually revert or cherry-pick.

Our extension never touches the user's working tree.  Every task runs
in a disposable git worktree on its own branch
(Section~\ref{sec:worktree-agent}).  When the task completes, we
present a per-hunk, per-file, and whole-task merge UI directly inside
VS~Code: the developer can accept or reject individual changes,
navigate between hunks with dedicated commands, or accept/reject all
changes in a file or across the entire task.  This gives the developer
the same granularity of control as a pull-request review, but embedded
in the editor and operating on changes the AI just produced seconds
ago.

No other assistant combines worktree-level isolation with an
inline merge review flow.  The closest analog is Aider's per-change
auto-commit, but that operates on the current branch and provides no
accept/reject UI---the developer must use standard git tooling to
inspect and revert individual commits.

%......................................................................
\subsection{Automatic Multi-Session Continuation}
\label{sec:continuation-feature}
%......................................................................

Context windows are finite, and complex tasks---large refactorings,
multi-file bug hunts, benchmark evaluations---routinely exceed them.
Existing assistants handle this by either truncating the conversation
(Copilot, Cursor) or asking the user to manually start a new session
and re-describe the task (Windsurf, Aider).  Devin operates in a
sandboxed environment with a single long context, but when the context
is exhausted, the task ends.

Our extension continues automatically.  The Relentless Agent
(Section~\ref{sec:relentless-agent}) detects when the context window
or step limit is approaching, serializes progress into a structured
summary, and spawns a new sub-session that picks up where the previous
one left off.  If a sub-session crashes, a separate summarizer agent
extracts useful context from the trajectory and feeds it to the next
attempt.  From the user's perspective, the task simply runs until it
succeeds, regardless of how many sub-sessions are needed.

%......................................................................
\subsection{Cross-Session Self-Improvement}
\label{sec:self-improvement-feature}
%......................................................................

Every AI assistant starts each session from scratch: the user must
re-explain project conventions, preferred patterns, and past decisions.
Some tools support a static configuration file (e.g.,
\texttt{.cursorrules} for Cursor, \texttt{AGENTS.md} or
\texttt{CLAUDE.md} for various agents), but these files must be
written and maintained by the developer.

Our extension maintains a \texttt{USER\_PREFS.md} file that the agent
reads at the start of each task and \emph{updates} at the end.  When
the agent discovers a new user preference or project invariant during
task execution---a naming convention, an architectural constraint, a
disliked pattern---it writes it to the file.  Crucially, the agent
also resolves conflicts: if a new preference contradicts an existing
one, the old entry is removed.  Over time, the file accumulates a
curated set of project-specific knowledge that makes the agent
progressively more effective without any manual configuration from the
developer.

%......................................................................
\subsection{Real-Time Budget Accountability}
\label{sec:budget-feature}
%......................................................................

AI coding assistants typically operate on a subscription model
(Copilot, Cursor) or a per-seat pricing model (Devin, Windsurf) that
obscures the per-task cost.  The developer has no visibility into how
many tokens a task consumed or how much it cost.

Our extension displays real-time cost tracking in the sidebar: input
tokens, output tokens, cache hits, dollar cost, and elapsed time are
updated at every agent step.  We enforce both per-task and global
budget ceilings.  If a task exceeds its budget, the agent raises a
hard error rather than silently accumulating charges.  This
transparency allows developers to make informed decisions about which
tasks to delegate to the AI and how to structure prompts for cost
efficiency.

%......................................................................
\subsection{Multi-Tab Concurrent Tasks}
\label{sec:multi-tab}
%......................................................................

Most AI coding assistants support only a single active task at a time.
Copilot Chat, Cursor's agent mode, and Windsurf process one request
before accepting the next.  Devin can run tasks in the background but
provides a separate web interface rather than IDE-native concurrency.

Our extension supports multiple concurrent tasks via a tabbed
interface in the sidebar.  Each tab runs an independent agent instance
with its own worktree, context window, and budget tracking.  The user
can start a refactoring task in one tab, switch to another tab to ask
an unrelated question, and return to find the refactoring still
running.  Per-tab state---DOM elements, pending user questions, merge
UI---is preserved across tab switches by detaching and re-attaching
per-tab DOM nodes rather than serializing and restoring values.

%......................................................................
\subsection{Integrated Browser Automation}
\label{sec:browser-feature}
%......................................................................

While some assistants can search the web (Devin, Perplexity-based
tools), none provide full programmatic browser control from within the
IDE.  Our extension includes a browser automation tool that allows the
agent to navigate to URLs, read accessibility trees, click elements,
type text, press keys, scroll, and take screenshots---all controlled
programmatically from within a VS~Code task.  We render a live browser
preview inside the extension's sidebar, allowing the developer to
watch the agent interact with web applications in real time.

This capability enables use cases that no other IDE assistant supports:
verifying a deployed web application after a code change, filling out
web forms as part of a testing workflow, scraping documentation to
inform a code generation task, or interacting with web-based developer
tools (CI dashboards, issue trackers) without leaving the editor.

%......................................................................
\subsection{Crash Recovery from Git State}
\label{sec:crash-recovery}
%......................................................................

If VS~Code crashes or the user restarts the editor mid-task, most AI
assistants lose all context: the conversation is gone, and any
partially applied changes are left in an indeterminate state in the
working tree.

Our extension stores all worktree state in git itself---branch names,
configuration entries, commit history---rather than in ephemeral
sidecar files.  On process restart, the agent queries git for any
pending branches matching its chat ID prefix and reconstructs all
instance attributes from git config.  The user can resume reviewing
and merging agent changes after a crash without any data loss.

%......................................................................
\subsection{Copilot Commit-Message Interception}
\label{sec:commit-interception}
%......................................................................

VS~Code's Source Control view exposes a sparkle button that invokes
\texttt{github.copilot.git.generateCommitMessage} to generate a
commit message using GitHub Copilot.  Our extension registers its own
handler for this command ID, intercepting the button so that our
agent generates the commit message instead.  This is a minor but
practical feature: it allows users who do not have a Copilot
subscription to still use the sparkle button, powered by whatever
LLM backend the extension is configured to use.

%----------------------------------------------------------------------
\section{Related Work}
\label{sec:related}
%----------------------------------------------------------------------

\textbf{Code generation agents.}
SWE-Agent~\citep{yang2024sweagent} and
OpenHands~\citep{wang2024openhands} provide LLM-based agents for
resolving software engineering tasks such as GitHub issues.  Both use
a single-session execution model without automatic continuation.
Agentless~\citep{xia2024agentless} takes the opposite approach,
showing that a simple two-phase localize-then-repair pipeline without
autonomous agent loops can achieve competitive results on
SWE-bench~\citep{jimenez2024swebench}.  Devin~\citep{devin2024}, an
industrial product marketed as ``the first AI software engineer,''
operates in a sandboxed environment with shell, browser, and editor
access.  Aider~\citep{aider2023} provides a terminal-based pair
programming interface with tight git integration, automatically
committing each change.  Our Relentless Agent layer addresses the
single-session limitation shared by most of these systems, while our
worktree isolation provides stronger safety guarantees than per-change
commits.

\textbf{ReAct and tool use.}
The ReAct framework~\citep{yao2023react} interleaves reasoning and
action.  Toolformer~\citep{schick2023toolformer} teaches models to use
tools via self-supervised learning.  We use native function calling
provided by modern LLM APIs rather than in-context tool
descriptions, which reduces prompt overhead and improves reliability.

\textbf{Reasoning and planning.}
Chain-of-thought prompting~\citep{wei2022chain} demonstrated that
eliciting step-by-step reasoning dramatically improves LLM performance
on complex tasks.  Tree of Thoughts~\citep{yao2024tree} generalizes
this to deliberate search over multiple reasoning paths.
Reflexion~\citep{shinn2023reflexion} introduces verbal reinforcement
learning, where an agent reflects on failed attempts and produces
self-critiques that improve subsequent trials.  Our continuation
protocol is conceptually related to Reflexion: failed sub-sessions
produce summaries that inform subsequent attempts.  However, we
operate at the level of full software
engineering tasks rather than isolated reasoning problems, and its
budget and step limits provide principled termination criteria.

\textbf{Multi-agent software development.}
ChatDev~\citep{qian2024chatdev} models the software development
process as a conversation between role-playing agents (CEO, CTO,
programmer, tester) organized in a waterfall-like pipeline.
MetaGPT~\citep{hong2024metagpt} takes a meta-programming approach,
encoding standard operating procedures as structured outputs that
coordinate specialized agents.
AutoGen~\citep{wu2023autogen} provides a general-purpose framework
for multi-agent conversation, enabling flexible topologies beyond
fixed pipelines.  These systems focus on generating entire
applications from scratch.  We take a different approach: rather than
simulating an organization of specialists, we use a
single agent with broad tool access and optional parallel sub-agents
for embarrassingly parallel sub-tasks, prioritizing practical utility
on real-world codebases over role-playing fidelity.

\textbf{Multi-turn autonomous agents.}
AutoGPT~\citep{autogpt2023} and BabyAGI~\citep{babyagi2023} implement
multi-step autonomous agents.  These systems typically lack budget
controls and safe code isolation.  Our layered architecture addresses
each of these concerns in a dedicated layer.

\textbf{Code-specialized language models.}
Beyond the general-purpose LLMs that our system can use as backends,
a rich line of work has produced models specifically trained for code.
Code Llama~\citep{roziere2023code} fine-tunes Llama~2 for code
generation and infilling.
StarCoder~\citep{li2023starcoder} trains on permissively licensed code
from GitHub with a fill-in-the-middle objective.
DeepSeek-Coder~\citep{guo2024deepseek} trains on a 2-trillion-token
corpus of code and natural language with a repository-level
context window.  Our system is model-agnostic and can leverage any of
these models through its pluggable LLM backend, benefiting from
advances in code-specialized pre-training without architectural
changes.

\textbf{Software engineering benchmarks.}
SWE-bench~\citep{jimenez2024swebench} evaluates agents on
real-world GitHub issues drawn from popular Python repositories,
requiring the agent to localize and fix bugs given only the issue
description.  It has become the de facto standard for measuring agent
capabilities in software engineering.
HumanEval~\citep{chen2021evaluating} and
MBPP~\citep{austin2021program} evaluate function-level code generation
from docstrings.  These benchmarks focus on isolated coding problems;
We target the broader workflow of multi-file, multi-step
software engineering tasks that require tool use, testing, and version
control.

\textbf{Agent frameworks and orchestration.}
LangChain~\citep{langchain2022} provides modular abstractions for
building LLM applications, including agent loops, tool integration,
and memory.  It focuses on composability and breadth of integrations
rather than on the specific concerns of software development.  Our
architecture is purpose-built for software engineering, with
each layer addressing a specific practical concern (budget tracking,
continuation, code safety) rather than providing general-purpose
primitives.

\textbf{LLM agent surveys.}
Several comprehensive surveys have mapped the rapidly growing
landscape of LLM-based agents.
\citet{xi2023rise} survey the design space of LLM agents along
three dimensions --- brain (reasoning), perception (input modalities),
and action (tool use) --- and catalog applications across social
science, natural science, and engineering.
\citet{wang2024survey} propose a systematic framework for autonomous
agents built on LLMs, covering profile, memory, planning, and action
modules.  Our system can be understood through the lens of these
frameworks: the KISS Agent implements the action loop, the Relentless
Agent addresses the memory and planning concerns through continuation
summaries, and the system prompt encodes the profile.

\textbf{IDE integration.}
GitHub Copilot~\citep{copilot2021}, Cursor~\citep{cursor2024}, and
Windsurf~\citep{windsurf2024} provide AI assistance within editors.
These tools typically operate at the level of code completion or
single-turn chat.  We operate at the level of autonomous
multi-step task execution with full tool access and git-level
isolation.

\textbf{Recent advances in agentic software engineering.}
The field has matured rapidly since late 2025.
\citet{hassan2025agentic} articulate the foundational pillars of
\emph{Agentic Software Engineering} (SE~3.0), defining a research
roadmap that emphasizes trust, controllability, and goal-oriented task
decomposition.  \citet{li2025rise} survey the landscape of autonomous
coding agents and characterize the transition from assistive code
completion to full-fledged AI teammates that initiate, plan, and
execute development tasks.  We instantiate several of the principles
advocated in these roadmaps, including layered controllability (via
budget tracking and step limits) and safe isolation (via worktrees).

\citet{wang2025agentic} provide a comprehensive survey of AI agentic
programming techniques, cataloging how LLM-based agents decompose
goals, interact with compilers and version control systems, and
self-correct through feedback loops.
\citet{chatlatanagulchai2025readmes} study \emph{agent context files}
--- persistent, project-level instruction files that guide agentic
coding tools --- and find that high-quality context files significantly
improve agent performance.  Our layered system prompt and
\texttt{SORCAR.md} override mechanism are instances of this pattern.
\citet{mohsenimofidi2025context} further investigate context
engineering for AI agents in open-source software, highlighting how
curated context improves agent efficacy on repository-level tasks.

\textbf{Evolving benchmarks for coding agents.}
SWE-bench Pro~\citep{deng2025swebenchpro} introduces a substantially
more challenging benchmark with 1,865 long-horizon problems drawn from
41 repositories, including commercial codebases, explicitly targeting
enterprise-level complexity beyond the original SWE-bench.  These
long-horizon tasks --- often requiring multi-file patches and hours of
professional developer effort --- directly motivate our continuation
mechanism.  \citet{prathifkumar2025swebenchverified}
raise the important question of benchmark contamination, showing that
overlap between SWE-Bench-Verified problems and LLM training data may
inflate scores, suggesting that high benchmark numbers may partly
reflect memorization rather than genuine problem-solving ability.
\citet{horikawa2025agentic} provide an empirical study of how
AI coding agents handle refactoring tasks, finding that while agents
can plan and execute complex refactorings, they still struggle with
cross-file dependency analysis --- a challenge that our sub-agent
parallelism partially addresses.

\textbf{Self-improvement and test-time scaling.}
\citet{robeyns2025selfimproving} demonstrate a self-improving coding
agent that iteratively refines its own scaffolding code, achieving
dramatic benchmark improvements through self-generated optimizations.
Our self-improvement loop (via \texttt{USER\_PREFS.md}) captures a
lighter-weight form of this idea: rather than rewriting its own code,
the agent accumulates learned user preferences and project
invariants across sessions.  \citet{gao2025trae} introduce the Trae
Agent, which applies test-time compute scaling to software engineering,
dynamically allocating more inference budget to harder problems.  Our
budget-tracking mechanism provides a complementary perspective: rather
than scaling compute adaptively, we enforce hard
budget ceilings while the Relentless Agent ensures maximum progress
within those bounds.

%----------------------------------------------------------------------
\section{Conclusion}
\label{sec:conclusion}
%----------------------------------------------------------------------

We have shown that a layered, single-concern architecture can address
the practical challenges of deploying LLM agents for real-world
software development.  The KISS Agent provides a robust execution core
with budget tracking.  The Relentless Agent eliminates the
context-window ceiling through automatic continuation.  The Sorcar
Agent equips the system with the tools a developer actually uses.  The
Chat Sorcar Agent enables multi-turn conversations that persist across
sessions.  The Worktree Sorcar Agent ensures that every task is safely
isolated in git, giving the developer full control over what gets
merged.

We complement the architecture with a system prompt that encodes
engineering discipline directly into the agent's behavior: read before
writing, test before fixing, plan before executing, verify before
finishing.  These are not novel insights --- they are the practices of
careful software engineering, translated into instructions that an LLM
can follow.

We make the source code publicly available at
\url{https://github.com/ksenxx/kiss_ai}.

%----------------------------------------------------------------------
% References
%----------------------------------------------------------------------

{
\small

\bibliographystyle{plainnat}

\begin{thebibliography}{99}

\bibitem[Chen et~al.(2021)]{chen2021evaluating}
Chen, M., Tworek, J., Jun, H., Yuan, Q., Pinto, H.~P., Kaplan, J.,
Edwards, H., Burda, Y., Joseph, N., Brockman, G., et~al.
\newblock Evaluating large language models trained on code.
\newblock {\em arXiv preprint arXiv:2107.03374}, 2021.

\bibitem[Rozi\`{e}re et~al.(2023)]{roziere2023code}
Rozi\`{e}re, B., Gehring, J., Gloeckle, F., Sootla, S., Gat, I.,
Tan, X.~E., Adi, Y., Liu, J., Remez, T., Rapin, J., et~al.
\newblock Code Llama: Open foundation models for code.
\newblock {\em arXiv preprint arXiv:2308.12950}, 2023.

\bibitem[Yao et~al.(2023)]{yao2023react}
Yao, S., Zhao, J., Yu, D., Du, N., Shafran, I., Narasimhan, K., and
Cao, Y.
\newblock ReAct: Synergizing reasoning and acting in language models.
\newblock In {\em International Conference on Learning
  Representations (ICLR)}, 2023.

\bibitem[Schick et~al.(2023)]{schick2023toolformer}
Schick, T., Dwivedi-Yu, J., Dess\`{i}, R., Raileanu, R., Lomeli, M.,
Zettlemoyer, L., Cancedda, N., and Scialom, T.
\newblock Toolformer: Language models can teach themselves to use
  tools.
\newblock In {\em Advances in Neural Information Processing Systems
  (NeurIPS)}, 2023.

\bibitem[Yang et~al.(2024)]{yang2024sweagent}
Yang, J., Jimenez, C.~E., Wettig, A., Liber, K., Narasimhan, K., and
Press, O.
\newblock {SWE-agent}: Agent-computer interfaces enable automated
  software engineering.
\newblock {\em arXiv preprint arXiv:2405.15793}, 2024.

\bibitem[Wang et~al.(2024)]{wang2024openhands}
Wang, X., Chen, Y., Yuan, L., Zhang, Y., Li, Y., Peng, H., and Ji,
H.
\newblock {OpenHands}: An open platform for {AI} software developers as
  generalist agents.
\newblock {\em arXiv preprint arXiv:2407.16741}, 2024.

\bibitem[{Significant Gravitas}(2023)]{autogpt2023}
{Significant Gravitas}.
\newblock {AutoGPT}.
\newblock \url{https://github.com/Significant-Gravitas/AutoGPT}, 2023.

\bibitem[Nakajima(2023)]{babyagi2023}
Nakajima, Y.
\newblock {BabyAGI}.
\newblock \url{https://github.com/yoheinakajima/babyagi}, 2023.

\bibitem[{GitHub}(2021)]{copilot2021}
{GitHub}.
\newblock {GitHub Copilot}: Your {AI} pair programmer.
\newblock \url{https://github.com/features/copilot}, 2021.

\bibitem[{Cursor}(2024)]{cursor2024}
{Cursor}.
\newblock {Cursor}: The {AI}-first code editor.
\newblock \url{https://cursor.sh}, 2024.

\bibitem[{Codeium}(2024)]{windsurf2024}
{Codeium}.
\newblock {Windsurf}: The {AI}-powered {IDE}.
\newblock \url{https://windsurf.com}, 2024.

\bibitem[Jimenez et~al.(2024)]{jimenez2024swebench}
Jimenez, C.~E., Yang, J., Wettig, A., Yao, S., Pei, K., Press, O.,
and Narasimhan, K.
\newblock {SWE-bench}: Can language models resolve real-world {GitHub}
  issues?
\newblock In {\em International Conference on Learning
  Representations (ICLR)}, 2024.

\bibitem[Xia et~al.(2024)]{xia2024agentless}
Xia, C.~S., Deng, Y., Dunn, S., and Zhang, L.
\newblock Agentless: Demystifying {LLM}-based software engineering
  agents.
\newblock {\em arXiv preprint arXiv:2407.01489}, 2024.

\bibitem[{Cognition Labs}(2024)]{devin2024}
{Cognition Labs}.
\newblock {Devin}: The first {AI} software engineer.
\newblock \url{https://devin.ai}, 2024.

\bibitem[Gauthier(2023)]{aider2023}
Gauthier, P.
\newblock {Aider}: {AI} pair programming in your terminal.
\newblock \url{https://github.com/paul-gauthier/aider}, 2023.

\bibitem[Wei et~al.(2022)]{wei2022chain}
Wei, J., Wang, X., Schuurmans, D., Bosma, M., Ichter, B., Xia, F.,
Chi, E., Le, Q., and Zhou, D.
\newblock Chain-of-thought prompting elicits reasoning in large
  language models.
\newblock In {\em Advances in Neural Information Processing Systems
  (NeurIPS)}, 2022.

\bibitem[Yao et~al.(2024)]{yao2024tree}
Yao, S., Yu, D., Zhao, J., Shafran, I., Griffiths, T.~L.,
Cao, Y., and Narasimhan, K.
\newblock Tree of thoughts: Deliberate problem solving with large
  language models.
\newblock In {\em Advances in Neural Information Processing Systems
  (NeurIPS)}, 2024.

\bibitem[Shinn et~al.(2023)]{shinn2023reflexion}
Shinn, N., Cassano, F., Gopinath, A., Narasimhan, K., and Yao, S.
\newblock Reflexion: Language agents with verbal reinforcement
  learning.
\newblock In {\em Advances in Neural Information Processing Systems
  (NeurIPS)}, 2023.

\bibitem[Qian et~al.(2024)]{qian2024chatdev}
Qian, C., Liu, W., Liu, H., Chen, N., Dang, Y., Li, J., Yang, C.,
Chen, W., Su, Y., Cong, X., Xu, J., Li, D., Liu, Z., and Sun, M.
\newblock {ChatDev}: Communicative agents for software development.
\newblock In {\em Proceedings of the 62nd Annual Meeting of the
  Association for Computational Linguistics (ACL)}, 2024.

\bibitem[Hong et~al.(2024)]{hong2024metagpt}
Hong, S., Zhuge, M., Chen, J., Zheng, X., Cheng, Y., Zhang, C.,
Wang, J., Wang, Z., Yau, S.~K.~S., Lin, Z., Zhou, L., Ran, C.,
Xiao, L., Wu, C., and Schmidhuber, J.
\newblock {MetaGPT}: Meta programming for a multi-agent collaborative
  framework.
\newblock In {\em International Conference on Learning
  Representations (ICLR)}, 2024.

\bibitem[Wu et~al.(2023)]{wu2023autogen}
Wu, Q., Bansal, G., Zhang, J., Wu, Y., Li, B., Zhu, E., Jiang, L.,
Zhang, X., Zhang, S., Liu, J., Awadallah, A.~H., White, R.~W.,
Burger, D., and Wang, C.
\newblock {AutoGen}: Enabling next-gen {LLM} applications via
  multi-agent conversation.
\newblock {\em arXiv preprint arXiv:2308.08155}, 2023.

\bibitem[Li et~al.(2023)]{li2023starcoder}
Li, R., Allal, L.~B., Zi, Y., Muennighoff, N., Kocetkov, D.,
Mou, C., Marone, M., Akiki, C., Li, J., Chim, J., et~al.
\newblock {StarCoder}: May the source be with you!
\newblock {\em Transactions on Machine Learning Research (TMLR)},
  2023.

\bibitem[Guo et~al.(2024)]{guo2024deepseek}
Guo, D., Zhu, Q., Yang, D., Xie, Z., Dong, K., Zhang, W.,
Chen, G., Bi, X., Wu, Y., Li, Y.~K., Luo, F., Xiong, Y., and
Liang, W.
\newblock {DeepSeek-Coder}: When the large language model meets
  programming --- the rise of code intelligence.
\newblock {\em arXiv preprint arXiv:2401.14196}, 2024.

\bibitem[Austin et~al.(2021)]{austin2021program}
Austin, J., Odena, A., Nye, M., Bosma, M., Michalewski, H.,
Dohan, D., Jiang, E., Cai, C., Terry, M., Le, Q., and Sutton, C.
\newblock Program synthesis with large language models.
\newblock {\em arXiv preprint arXiv:2108.07732}, 2021.

\bibitem[{LangChain}(2022)]{langchain2022}
{LangChain}.
\newblock {LangChain}: Build context-aware reasoning applications.
\newblock \url{https://github.com/langchain-ai/langchain}, 2022.

\bibitem[Xi et~al.(2023)]{xi2023rise}
Xi, Z., Chen, W., Guo, X., He, W., Ding, Y., Hong, B., Zhang, M.,
Wang, J., Jin, S., Zhou, E., et~al.
\newblock The rise and potential of large language model based agents:
  A survey.
\newblock {\em arXiv preprint arXiv:2309.07864}, 2023.

\bibitem[Wang et~al.(2024b)]{wang2024survey}
Wang, L., Ma, C., Feng, X., Zhang, Z., Yang, H., Zhang, J.,
Chen, Z., Tang, J., Chen, X., Lin, Y., Zhao, W.~X., Wei, Z., and
Wen, J.
\newblock A survey on large language model based autonomous agents.
\newblock {\em Frontiers of Computer Science}, 18(6):186345, 2024.

\bibitem[Hassan et~al.(2025)]{hassan2025agentic}
Hassan, A.~E., Li, H., Lin, D., and Adams, B.
\newblock Agentic software engineering: Foundational pillars and a
  research roadmap.
\newblock {\em arXiv preprint arXiv:2509.06216}, 2025.

\bibitem[Li et~al.(2025)]{li2025rise}
Li, H., Zhang, H., and Hassan, A.~E.
\newblock The rise of {AI} teammates in software engineering ({SE}~3.0):
  How autonomous coding agents are reshaping software engineering.
\newblock {\em arXiv preprint arXiv:2507.15003}, 2025.

\bibitem[Deng et~al.(2025)]{deng2025swebenchpro}
Deng, X., Da, J., Pan, E., He, Y.~Y., Ide, C., Garg, K.,
Lauffer, N., Park, A., Pasari, N., Rane, C., et~al.
\newblock {SWE-Bench Pro}: Can {AI} agents solve long-horizon software
  engineering tasks?
\newblock {\em arXiv preprint arXiv:2509.16941}, 2025.

\bibitem[Prathifkumar et~al.(2025)]{prathifkumar2025swebenchverified}
Prathifkumar, T., Mathews, N.~S., and Nagappan, M.
\newblock Does {SWE-Bench-Verified} test agent ability or model memory?
\newblock {\em arXiv preprint arXiv:2512.10218}, 2025.

\bibitem[Horikawa et~al.(2025)]{horikawa2025agentic}
Horikawa, K., Li, H., Kashiwa, Y., and Adams, B.
\newblock Agentic refactoring: An empirical study of {AI} coding agents.
\newblock {\em arXiv preprint arXiv:2511.04824}, 2025.

\bibitem[Wang et~al.(2025)]{wang2025agentic}
Wang, H., Gong, J., Zhang, H., Xu, J., and Wang, J.
\newblock {AI} agentic programming: A survey of techniques, challenges,
  and opportunities.
\newblock {\em arXiv preprint arXiv:2508.11126}, 2025.

\bibitem[Chatlatanagulchai et~al.(2025)]{chatlatanagulchai2025readmes}
Chatlatanagulchai, W., Li, H., Kashiwa, Y., and Reid, B.
\newblock Agent {README}s: An empirical study of context files for
  agentic coding.
\newblock {\em arXiv preprint arXiv:2511.12884}, 2025.

\bibitem[Mohsenimofidi et~al.(2025)]{mohsenimofidi2025context}
Mohsenimofidi, S., Galster, M., and Treude, C.
\newblock Context engineering for {AI} agents in open-source software.
\newblock {\em arXiv preprint arXiv:2510.21413}, 2025.

\bibitem[Robeyns et~al.(2025)]{robeyns2025selfimproving}
Robeyns, M., Szummer, M., and Aitchison, L.
\newblock A self-improving coding agent.
\newblock {\em arXiv preprint arXiv:2504.15228}, 2025.

\bibitem[Gao et~al.(2025)]{gao2025trae}
Gao, P., Tian, Z., Meng, X., and {Trae Research Team}.
\newblock Trae Agent: An {LLM}-based agent for software engineering
  with test-time scaling.
\newblock {\em arXiv preprint arXiv:2507.23370}, 2025.

\end{thebibliography}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage
\input{checklist.tex}

\end{document}
